Stats

### 2022-03-23 stats/analysis.Rmd
fix calculation clickDistInBalloons
play around with nr of replications splithalfr

    # distance between target and click in balloon widths (balloon width is 160 SVG units)
    clickDistInBalloons = clickDistInBalloons,
  )
```

@@

# odd even split
splitscores_hedge_oddeven_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 10000,
  method = c("odd_even"),
)

@@

# odd even split with stratification by target position
splitscores_hedge_oddevenStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
  replications = 10000,
  method = c("odd_even"),
)

@@

# first second testhalves split
splitscores_hedge_firstsecond_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 10000,
  method = c("first_second"),
)

@@

# first second testhalves split with stratification by target position
splitscores_hedge_firstsecondStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
  replications = 10000,
  method = c("odd_even"),
)

@@

# odd even split
splitscores_hedge_oddeven_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 10000,
  method = c("odd_even"),
)

@@

# odd even split with stratification by target position
splitscores_hedge_oddevenStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
  replications = 10000,
  method = c("odd_even"),
)

@@

# first second testhalves split
splitscores_hedge_firstsecond_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 10000,
  method = c("first_second"),
)

@@

# first second testhalves split with stratification by target position
splitscores_hedge_firstsecondStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
  replications = 10000,
  method = c("odd_even"),
)

@@

# odd even split
splitscores_box_oddeven_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 10000,
  method = c("odd_even"),
)

@@

# odd even split with stratification by target position
splitscores_box_oddevenStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
  replications = 10000,
  method = c("odd_even"),
  careful = FALSE
)

@@

# first second testhalves split
splitscores_box_firstsecond_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 10000,
  method = c("first_second"),
)

@@

# first second testhalves split with stratification by target position
splitscores_box_firstsecondStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
  replications = 10000,
  method = c("odd_even"),
  careful = FALSE,
)

@@

# odd even split
splitscores_box_oddeven_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 10000,
  method = c("odd_even"),
)

@@

# odd even split with stratification by target position
splitscores_box_oddevenStrat_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
  replications = 10000,
  method = c("odd_even"),
  careful = FALSE,
)

@@

# first second testhalves split
splitscores_box_firstsecond_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 10000,
  method = c("first_second"),
)

@@

# first second testhalves split with stratification by target position
splitscores_box_firstsecondStrat_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
  replications = 10000,
  method = c("odd_even"),
  careful = FALSE,
)

>>>>

    # distance between target and click in balloon widths (balloon width is 160 SVG units)
    clickDistInBalloons = abs(clickDistFromTargetCenterX)/160,
  )
```

@@

# odd even split
splitscores_hedge_oddeven_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("odd_even"),
)

@@

# odd even split with stratification by target position
splitscores_hedge_oddevenStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
  replications = 1,
  method = c("odd_even"),
)

@@

# first second testhalves split
splitscores_hedge_firstsecond_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("first_second"),
)

@@

# first second testhalves split with stratification by target position
splitscores_hedge_firstsecondStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
  replications = 1,
  method = c("odd_even"),
)

@@

# odd even split
splitscores_hedge_oddeven_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("odd_even"),
)

@@

# odd even split with stratification by target position
splitscores_hedge_oddevenStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
  replications = 1,
  method = c("odd_even"),
)

@@

# first second testhalves split
splitscores_hedge_firstsecond_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("first_second"),
)

@@

# first second testhalves split with stratification by target position
splitscores_hedge_firstsecondStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
  replications = 1,
  method = c("odd_even"),
)

@@

# odd even split
splitscores_box_oddeven_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("odd_even"),
)

@@

# odd even split with stratification by target position
splitscores_box_oddevenStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
  replications = 1,
  method = c("odd_even"),
  # careful = FALSE
)

@@

# first second testhalves split
splitscores_box_firstsecond_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("first_second"),
)

@@

# first second testhalves split with stratification by target position
splitscores_box_firstsecondStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
  replications = 1,
  method = c("odd_even"),
  # careful = FALSE,
)

@@

# odd even split
splitscores_box_oddeven_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("odd_even"),
)

@@

# odd even split with stratification by target position
splitscores_box_oddevenStrat_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
  replications = 1,
  method = c("odd_even"),
  # careful = FALSE,
)

@@

# first second testhalves split
splitscores_box_firstsecond_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("first_second"),
)

@@

# first second testhalves split with stratification by target position
splitscores_box_firstsecondStrat_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
  replications = 1,
  method = c("odd_even"),
  # careful = FALSE,
)
